Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2016-10-31 ms_pre_post.Rmd
Edit through Model: Polyandry

@@

After costs are paid, each remaining female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$). The exact value of $N_{males}$ is calculated by randomly sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$. This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$. A value of one is added to $P_{p}$ to ensure that all females that have not paid a cost choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.

The value of $P_{p}$ is affected by the summed values of a focal female's 20 $P_{a}$ alleles. Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage. Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014]. The tendency for polyandry genotype $P_{g}$ is therefore defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive. However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative. Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero). The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to polyandry. Negative genotype values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females. In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).

>>>>

After costs are paid, each remaining female chooses $N_{males}$ males to mate with, where $N_{males}$ is calculated by sampling from a Poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$. This ensures that all surviving females choose at least one mate, and causes some stochastic variation aroudn the expected mean $N_{males}$ of $P_{p}+1$. A female's value of $P_{p}$ depends on the sum of her 20 $P_{a}$ allele values, which might be negative or positive. However, because females cannot mate with a negative number of males, $P_{p}$ is constrained to be zero or positive such that $P_{p} = 0$ when $P_{g} < 0$, but $P_{p} = P_{g}$ when $P_{g} \geq 0$. Polyandry is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998; @Duthie] that is influenced by continuous genetic variation but only expressed at the threshold value of $P_{g} > 0$. Any negative $P_{g}$ value therefore generates phenotypic monandry, while positive $P_{g}$ values can lead to different degrees of realised polyandry (i.e., different numbers of mates, $N_{males}$).

@@
